results

### 2020-10-22 analysis/007_invoice_exploration.Rmd
subject exploration
cc licenses per sponsorship type

---
title: "invoice analysis"
output: html_document
---

@@

```{r}
# load eligible oa articles
hybrid_volume <- readr::read_csv(here::here("data", "hybrid_volume_eligible.csv"))

# aggregate data
sponsored_articles <- hybrid_volume %>%
  mutate(oa_sponsor_type = ifelse(is.na(oa_sponsor_type), "unknown", oa_sponsor_type)) %>%
  mutate(oa_sponsor_type = recode(oa_sponsor_type, 
                                  `FundingBody` = "Agreement",
                                  `ElsevierWaived` = "Fee Waived")) %>%
  mutate(fct_source = fct_infreq(oa_sponsor_type)) %>%
  mutate(fct_source = fct_lump(fct_source, prop = 0.05)) %>%
  count(issued_year, fct_source)
all_articles <- hybrid_volume %>%
  group_by(issued_year) %>%
  summarise(n = n())
```

@@

```{r invoiceoverview, fig.cap="Development of fee-based open access publishing in Elsevier hybrid journals by invoicing type. Colored bars represent the invoice recipient, or whether the fee was waived. Grey bars show the total number of hybrid open access articles published in Elsevier journals from 2015 to date."}
# plot
ggplot(sponsored_articles, aes(x = gsub("20", "'", issued_year), y = n)) +
  geom_bar(
    data = all_articles,
    aes(fill = "All hybrid OA"),
    color = "transparent",
    stat = "identity"
  ) +
  geom_bar(aes(fill = "by invoicing type"), color = "transparent", stat = "identity") +
  facet_wrap( ~ fct_source, nrow = 1) +
  scale_fill_manual(values = c("#b3b3b3a0", "#56B4E9"), name = "") +
  labs(x = NULL, y = NULL) + 
  scale_y_continuous(labels = scales::number_format(big.mark = " "),
                      expand = expansion(mult = c(0, 0.05))) + theme_minimal_hgrid() +
  theme(legend.position="top", legend.justification = "right")
```

>>>>

---
title: "invoice analysis"
output: github_document
---

@@

```{r}
# load eligible oa articles
hybrid_volume <- readr::read_csv(here::here("data", "hybrid_articles.csv"))

# aggregate data
sponsored_articles <- hybrid_volume %>%
  mutate(oa_sponsor_type = ifelse(is.na(oa_sponsor_type), "unknown", oa_sponsor_type)) %>%
  mutate(oa_sponsor_type = recode(oa_sponsor_type, 
                                  `FundingBody` = "Agreement",
                                  `ElsevierWaived` = "Fee Waived")) %>%
  mutate(fct_source = fct_infreq(oa_sponsor_type)) %>%
  mutate(fct_source = fct_lump(fct_source, prop = 0.05)) %>%
  mutate(cc_norm = ifelse(grepl("/by/", URL), "cc-by", "cc-by-nc-nd")) %>%
  count(issued_year, fct_source, cc_norm)
all_articles <- hybrid_volume %>%
  group_by(issued_year) %>%
  summarise(n = n())
```

@@

```{r invoiceoverview, fig.cap="Development of fee-based open access publishing in Elsevier hybrid journals by invoicing type. Colored bars represent the invoice recipient, or whether the fee was waived. Grey bars show the total number of hybrid open access articles published in Elsevier journals from 2015 to date."}
# plot
ggplot(sponsored_articles, aes(x = gsub("20", "'", issued_year), y = n), alpha = 0.8) +
  geom_bar(
    data = all_articles,
    color = "transparent",
    stat = "identity",
    fill = "#b3b3b3a0"
  ) +
  geom_bar(aes(fill = cc_norm), color = "white", stat = "identity", alpha = 0.8, size = 0.25,
           position = position_stack(reverse = T)) +
  facet_wrap( ~ fct_source, nrow = 1) +
  scale_fill_manual(values = 
                      c(`cc-by` = "#B52141",
                        `cc-by-nc-nd` = "#0093c7"),
                    name = "CC license variant") +
  labs(x = NULL, y = NULL) + 
  scale_y_continuous(labels = scales::number_format(big.mark = " "),
                      expand = expansion(mult = c(0, 0.05))) + theme_minimal_hgrid() +
  theme(legend.position="top", legend.justification = "right")
```

### 2020-10-22 analysis/results.Rmd
cc licenses per sponsorship type

---
bibliography: references.bib
csl: chicago.csl
output: html_document
always_allow_html: true
---

@@

# aggregate data
sponsored_articles <- hybrid_volume %>%
  mutate(oa_sponsor_type = ifelse(is.na(oa_sponsor_type), "unknown", oa_sponsor_type)) %>%
  mutate(oa_sponsor_type = recode(oa_sponsor_type, 
                                  `FundingBody` = "Agreement",
                                  `ElsevierWaived` = "Fee Waived")) %>%
  mutate(fct_source = fct_infreq(oa_sponsor_type)) %>%
  mutate(fct_source = fct_lump(fct_source, prop = 0.05)) %>%
  count(issued_year, fct_source)
all_articles <- hybrid_volume %>%
  group_by(issued_year) %>%
  summarise(n = n())
```

>>>>

---
bibliography: references.bib
csl: chicago.csl
output: 
  github_document
always_allow_html: true
---

@@

# aggregate data
sponsored_articles <- hybrid_volume %>%
  mutate(oa_sponsor_type = ifelse(is.na(oa_sponsor_type), "unknown", oa_sponsor_type)) %>%
  mutate(oa_sponsor_type = recode(oa_sponsor_type, 
                                  `FundingBody` = "Agreement",
                                  `ElsevierWaived` = "Fee Waived")) %>%
  mutate(fct_source = fct_infreq(oa_sponsor_type)) %>%
  mutate(fct_source = fct_lump(fct_source, prop = 0.05)) %>%
  mutate(cc_norm = ifelse(grepl("/by/", URL), "cc-by", "cc-by-nc-nd")) %>%
  count(issued_year, fct_source, cc_norm)
all_articles <- hybrid_volume %>%
  group_by(issued_year) %>%
  summarise(n = n())
```
